Beyond query expansion - expanding documents for fluid keyword search

### 2020-10-09 IUI2021/paper.tex
generate.rbは実験中...

\def\GH{\textsf{GitHelp}}
\def\GIT{\texttt{git}}
\def\EH{\textsf{ExpandHelp}}
\def\SB{\textsf{Scrapbox}}
\long\def\tt#1{\texttt{#1}}
\long\def\stt#1{\texttt{\fontsize{9pt}{0pt}\selectfont{#1}}}
\long\def\sf#1{\textsf{#1}}
\long\def\ssf#1{\textsf{\fontsize{9pt}{0pt}\selectfont{#1}}}
\long\def\qtt#1{``\tt{#1}''}   % quote tt
\long\def\sqtt#1{``\stt{#1}''} % small quote tt
\long\def\qsf#1{``\sf{#1}''}
\long\def\sqsf#1{``\ssf{#1}''}
\long\def\qit#1{``\textit{#1}''}
\long\def\smallfont{\fontsize{9pt}{0pt}\selectfont}

@@

  As we have shown before, one of the big reasons why we fail to find a document is that
  the user's search keyword does not exist in the document.
  Providing entries for ExpandSearch can solve the problem, but

@@

@@

We have been applying ExpahdSearch for various customer support services on existing Web services.
The help system based on ExpandSearch is called \textit{Helpfeel}, and

Helpfeel is a FAQ engine that supports users who do not have enough vocabulary for the Web services they want to use.

@@

Figure xxx shows an example Helpfeel page that supports finding FAQs
for PayPay Free market run by Yahoo! Japan.
We provide the description on the Scrapbox wiki service,

@@

We created the GitHelp system using ExpandHelp, so that git users can easily
remember command options and use it without perfectly remembering the git commands.

----------------------------

We implemented the {\GH} system
with which a user can translate his vague intention in various languages
into a complete {\GIT} command
using the {\EH} framework.

\begin{figure}[h]
  {\smallfont
  \verb|$ git diff HEAD^^ README.md|
  \par
  \verb|$|
  }
  \caption{Invoking \stt{git diff}.}
  \label{gitdiff}
\end{figure}

% \begin{quotation}
%   {\smallfont
%   \verb|$ git diff HEAD^^ README.md|
%   \par
%   \verb|$|
%   }
% \end{quotation}

If {\GH} is installed,
the user can type a special shortcut key
% (e.g. \tt{Cmd-Ctrl-G})
to invoke {\GH} after typing \sqtt{git RE 2} to see how he can
perform the task.

\begin{figure}[h]
  % \includegraphics[width=9cm,bb=0 0 1194 822]{figures/example1.png}
  \includegraphics[width=9cm,bb=0 0 900 600]{../../GitHelp/paper/figures/example1.png}
  %\includegraphics[width=9cm,bb=0 0 1000 600]{figures/githelp_e2.png}
  \caption{Invoking {\GH} after typing \stt{git read 2}.}
  \label{example1}
\end{figure}

Here, various candidate entries with
descriptions and command strings are listed,
just like text input support systems for non-English languages.
One of the entries says
``\ssf{Compare} \stt{README.md} \ssf{with the one from 2 versions before}'',
and if the user thinks that's what he wants to do,
he can select the entry by typing arrow keys and type the enter key.
Then the user's input string is replaced by the right command string
that satisfies the user's need.

When the user types a special shortcut key
after typing \sqtt{git sh reed 3},
entries related to \stt{README.md} file are listed because
\sqtt{reed} is close to \sqtt{README.md}.

\begin{figure}[h]
  %\includegraphics[width=9cm,bb=0 0 1100 760]{figures/example2.png}
  \includegraphics[width=9cm,bb=-100 0 800 550]{../../GitHelp/paper/figures/example2.png}
  \caption{Invoking {\GH} after typing \stt{git sh reed 3}.}
  \label{example2}
\end{figure}

A Japanese {\GIT} user can do the same thing just like
1vEnglish-speaking users (Figure \ref{example3}).
He can use the term \qtt{表}, etc. to find how he can perform the job.

\begin{figure}[t]
  % bb=0 0 1290 866
  % \includegraphics[width=12cm,bb=-100 -100 1190 766]{figures/githelp1.png}
  \includegraphics[width=12cm,bb=-100 -100 1190 766]{../../GitHelp/paper/figures/example4.png}
  \caption{Invoking {\GH} in Japanese environment.}
  \label{example3}
\end{figure}

\begin{figure}[t]
% \centerline{\includegraphics[width=100mm,bb=0 0 1428 1288]{figures/scrapbox1.png}}
  \centerline{\includegraphics[width=100mm,bb=-50 -50 1100 950]{../../GitHelp/paper/figures/scrapbox3.png}}
  \caption{A {\SB} page for \tt{git diff}.}
  \label{scrapboxpage}
\end{figure}

\subsection{OmniHelp}

OmniHelp is an implementation of ExpandHelp that runs on Chrome browser.
The URL window on Chrome is called omnibox,

\begin{verbatim}
[[ExpandSearchの実例]]
 まず実例を紹介する。実装はあとで。[[評価実験にもなっている。]]
[[実例1]] ExpandHelpの実際の利用
 ScrapboxというWiki上にいろんな表現を用意しておく
 Helpfeel
  PayPayフリマなどですごく効率があがった
 実際これによりヘルプ問い合わせは劇的に減る (出典: Helpfeel)
[[実例2]] 検索インタフェースの融合
 マイHelpfeel
 検索をひとつの方法に統合する
  検索方法が複数だと面倒臭い
   ググって出なければ逆引き辞典を検索する、みたいなのは面倒
  同じ検索インタフェースでいろんなところを探すほうが簡単である
  どこにメモしたか忘れて困ることがなくなる
 自分のデータが増えていく状況のグラフを書ける!

[[実例3]]
 gitのヘルプ - コマンドラインで動くもの
  パラメタを指定して実行につなげることすらできる
\end{verbatim}

@@

\subsection{ExpandHelp}

A flexible help data retrieval mechanism ``{\EH}'' is used in {\GH}.
%
Help data used in {\EH} are provided as a set of data entries
consisting of a regular expression that represents description of the help entry
and a corresponding command pattern string.
A description string is used to produce natural language texts
that are easily understandable by users,
while command patterns represents the generated command string
corresponding to the description.
%
For example, a help entry for showing the difference between
current file and older file can be defined like this:

\begin{quote}
  \textbf{description}: \\
  \stt{Compare (\#\{files\}) with the one from (1|2|3|4) versions before}\\
  \textbf{command}: \\
  {\smallfont\verb|git diff $(git rev-list -n #{$2} HEAD -- #{$1})^|} \\
  {\smallfont\verb| -- #{$1}|}
\end{quote}

@@

can be used for Japanese users.
In this case,
\sqsf{README.mdを1個前のものと比較する},
\sqsf{README.mdを2個前のものと比較する}, etc.
are used for the matching.

@@

Regular expressions are widely used for finding patterns in text strings
in modern programming languages and in the Unix environment.
In {\EH}, we use regular expressions for
generating various patterns of descriptions from a short specification.
For example, we use a short regular expression
\sqtt{(remove|delete|erase) (data|file)}
for representing expressions like
\sqsf{remove data},\sqsf{erase file}, etc.

Converting a regular expression to a state transition machine is a
straightforward task.
When we have a regular expression
\sqtt{Compare (README.md|index.html|package.json) with the one (1|2|...|10) versions before}, 
we can convert it into a state transition diagram
shown in Figure \ref{statemachine1}.

\begin{figure}[htb]
\includegraphics[width=90mm,bb=0 0 571 126]{figures/statemachine.pdf}
\caption{State transition diagram for a \stt{git} command description.}
\label{statemachine1}
\end{figure}

@@

Using the state transition diagram shown in Figure \ref{statemachine1},
{\EH} generates all the strings represented in the regular expressions,
and filter them by the pattern provided by the user.

We can generate texts from a state transition diagram by traversing nodes one by one.
Starting at the start node
(\raisebox{-2pt}{\includegraphics[height=10pt,bb=0 0 40 40]{figures/startnode.pdf}})
in Figure \ref{statemachine1},
we can visit other nodes via edges and generate a tree of generated texts
shown in Figure \ref{gentree1}.
After visiting the initial node
\raisebox{-2pt}{\includegraphics[height=10pt,bb=0 0 40 40]{figures/startnode.pdf}},
the system generates a string \sqsf{Compare} and proceeds to the next node.
In the second generation,
the system can add \sqsf{README.md}, \sqsf{index.html}, and \sqsf{package.json}
to \sqsf{Compare}, generating
\sqsf{Compare README.md}, \sqsf{Compare index.html}, etc.
The system can repeat finding edges from previously visited nodes,
and eventually generates all the strings described above.
Of course, it is impossible to generate all the strings
from a regular expression like ``\tt{(0|1)+}'' that represents infinite length of
strings consisting of \tt{0}s and \tt{1}s, so the generation should be
terminated at a certain generation.

\begin{figure}[htb]
\includegraphics[width=85mm,bb=0 0 643 398]{figures/gentree1.pdf}
\caption{Generating a text tree from a state transition machine.}
\label{gentree1}
\end{figure}

@@

Similarly in our case,
it is not efficient to perform the matching operation
after generating all the texts from the regular expression,
and it is better to calculate the matching
at the time of generating each text.
We call it the \qit{generate-and-filter} strategy,
and implemented the algorithm in {\EH}.
Unlike simple puzzle problems where
conditions are strict and finding one solution is enough,
our goal is to find help description strings
that fits the query pattern while allowing errors.
For this goal,
the system should perform approximate pattern matching
without sacrificing processing speed.
%
We could implement flexible generate-and-filter by using a simple and efficient
approximate pattern matching algorithm based on the ``shifter algorithm''.

@@

\begin{figure}[h]
  \centerline{\includegraphics[width=50mm,bb=0 0 439 73]{figures/readme1.pdf}}
  \caption{A state machine for \qsf{README}.}
  \label{readme1}
\end{figure}

@@

\begin{figure}[h]
  \centerline{\includegraphics[width=50mm,bb=0 0 439 73]{figures/readme2.pdf}}
  \caption{After receiving \qsf{R}.}
  \label{readme2}
\end{figure}

@@

%   *  ** 
%  risto rante
%  restaurant
% \begin{figure}[htb]
%   \centerline{\includegraphics[width=30mm,bb=0 0 104 51]{figures/readme-mismatch.pdf}}
%   \caption{Matching error between \qsf{README} and \qsf{REEDEE}.}
%   \label{readme-reddy-mismatch}
% \end{figure}

@@

\begin{figure}[htb]
  \centerline{\includegraphics[width=60mm,bb=0 0 443 282]{figures/readme-ambig.pdf}}
  \caption{A pattern matcher accepting 0-3 errors.}
  \label{shifterambig}
\end{figure}

@@

\begin{figure}[htb]
  \centerline{\includegraphics[width=60mm,bb=0 0 443 282]{figures/readme-reedee.pdf}}
  \caption{Accepting \sqsf{REEDEE}'' using a matcher for \sqsf{README}.}
  \label{readme-reedee}
\end{figure}

@@

\begin{figure}[htb]
  \centerline{\includegraphics[width=50mm,bb=0 0 302 230]{figures/RE_2.pdf}}
  \caption{A pattern matcher for \sqtt{REE 2}.}
  \label{RE_2}
\end{figure}

\begin{figure*}[bth]
\centerline{\includegraphics[width=110mm,bb=0 0 643 446]{figures/gentree2.pdf}}
\caption{Matching statuses for \sqtt{REE 2} associated with text generation nodes.}
\label{gentree2}
\end{figure*}

@@

% \begin{figure*}[bt]
% \centerline{\includegraphics[width=146mm]{figures/04ad7dee5679450e5390821745b5a0b7.png}}
% \caption{A portion of the help data in Ruby.}
% \label{helpdata}
% \end{figure*}

@@

The data used in {\GH} are represented as ``{\SB}'' documents
shown in Figure \ref{scrapboxpage}.
%
{\SB} is a general-purpose real-time Wiki system for data sharing.
{\SB} users can edit the contents of Wiki pages directly
on Web browsers just like using text editors.

% \begin{figure}[htb]
% \begin{verbatim}
% \end{verbatim}
% % \centerline{\includegraphics[width=100mm,bb=0 0 1428 1288]{figures/scrapbox1.png}}
% \centerline{\includegraphics[width=100mm,bb=-50 -50 1000 900]{figures/scrapbox1.png}}
% \caption{A {\SB} page for \tt{git diff}.}
% \label{xxxxx}
% \end{figure}

This page shows how to use \sqtt{git diff}, and
the page contains command specifications in {\EH} format
in addition to the documentation.

@@

Also, since the database is on the Wiki page, any member of the
Wiki can correct the document or add additional {\GH} specifications.
When a user could not get a good support from {\GH}, he can add
{\EH} specifications to the {\SB} document himself
so that he and other people can get better support
from {\GH} next time.

@@

There have long been many researches on
intelligent help systems\cite{Delisle:2002:UIH:606412.606415},
but few number of projects seem to be going on these days,
maybe because now we can use the Internet for getting intelligent help from
real people,
either by searching existing Web pages or 
by asking in user forums like StackOverflow\footnote{
  \textsf{https://stackoverflow.com/}
}.
Information on the net is rich these days, and we can easily
find somebody who can give good answers to our questions.
This is a good news, but 
asking many trivial questions on the net is not considered to be a
good manner, and
using a powerful and flexible local help system like {\EH} is
preferable most of the time.

@@

\begin{figure}[H]
  % \includegraphics[width=8cm,bb=0 0 976 670]{figures/nyuuryoku-ime.png}
  \centerline{\includegraphics[width=8cm,bb=0 0 976 670]{figures/nyuuryoku-ime.png}}
  \caption{An IM for Japanese text input.}
  \label{gyaim}
\end{figure}

@@

IMs are very popular in the modern computing environment in the world
and it is very common for people to 
use translation systems for using computers.
%
The behavior of {\GH} is similar to conventional IMs, and
integration of multiple IM-like systems should be challenged in the future.

@@

Gitsome\footnote{\textsf{https:{\slash}{\slash}github.com{\slash}donnemartin{\slash}gitsome}}
helps {\GIT} users by
dynamically showing possible arguments and related manuals on the Unix shell,
just like {\GH} does.
The goal of Gitsome is almost the same as {\GH} and we agree with its concept,
but Gitsome does not support flexible approximate matching and
help data sharing.

@@

Han's Abbreviation Completion system\cite{Han:2009:CCA:1747491.1747530}
can generate a code snippet from abbreviation strings give by the user.
For example, a code snippet like \sqtt{chooser. showOpenDialog()}
can be generated from strings like
\sqsf{ch} and \sqsf{opn}, using the code database and HMM.
It can be very useful as a shorthand for handling long names,
but users should have a vague knowledge about the correct names
(e.g. \sqtt{chooser}, \sqtt{dialog}),
and large code example corpus should exist before being able to
create the database.
{\EH} database can be created by hand at the time of the system development
and no corpus is required.

@@

Using BluePrint\cite{Brandt:2010:EPI:1753326.1753402}
as a plugin for Adobe Flex Builder,
users can search sample codes from the Web and use it immediately.
%   サンプルコードをすぐ参照して利用できる[IDE]
%
HelpMeOut\cite{Hartmann:2010:OPS:1753326.1753478} tells users
how to handle compile errors,
based on the people's experiences of handling compile errors.
%
Resources on the net are precious, and such data can be
easily incorporated to {\EH} databases.

@@

Since the translation mechanism of {\EH} is simple and flexible,
it can be used for a wide range of application domains where
intelligent help is required.
{\EH} is actually used as the help page for
one of our Web services, hoping that
novice users can easily find the feature they need.
When a user submits a query that includes vocabularies
not in the {\EH} document,
we are able to add them to the {\SB} database easily.

Figure \ref{mac1} and Figure \ref{mac2} shows how
{\EH} can be used as a launcher for MacOS.
Like {\GH}, users can execute concrete commands only by
showing small fragments of their intentions to the system.

\begin{figure}[h]
  %\centerline{\includegraphics[width=8cm,bb=0 0 397 247]{figures/clock.png}}
  \centerline{\includegraphics[width=8cm,bb=0 0 300 200]{figures/mac1.png}}
  \caption{Using {\EH} in the menu bar of MacOS.}
  \label{mac1}
\end{figure}

\begin{figure}[h]
  %\centerline{\includegraphics[width=8cm,bb=0 0 392 185]{figures/mac2.png}}
  \centerline{\includegraphics[width=8cm,bb=0 0 300 130]{figures/mac2.png}}
  \caption{Using {\EH} in the menu bar of MacOS.}
  \label{mac2}
\end{figure}

@@

Using a command shell,
users have to enter a command first and enter options and arguments after that.
Using a GUI desktop,
users can right-click a data icon to show a menu,
and select what he wants to do from the menu.
Switching between command-oriented usage pattern and
data-oriented usage pattern is sometimes confusing.
Using {\EH}, users can find what they can do
either by specifying commands or by specifying data, 
without worrying about the order.

@@

An advantage of using a regular expression is that
it is fairly easy for users to write description texts.
People can easily write a help description like
\sqtt{(Start|Run) Firefox browser}
without having a knowledge of automata or formal grammar.
We can use arbitrary texts for the database of {\EH}.
For example,
we can collect hundreds of books titled ``Windows tips'' from the market
and convert all the title of the tips into help data of {\EH}.

@@

We proposed the ``translation paradigm'' for bridging the gap between
users' intention and actual operations.
%
We have introduced a general-purpose flexible framework {\EH}
that can translate fragments of user's vague intentions into
concrete command strings required to control computers and
other complex artifacts.
We showed the principles and applications of {\EH} by using it
for {\GH}, a help system for supporting {\GIT} users
based on the shared database that any user can edit to share
translation knowledge between users.
%
{\EH} framework is useful for any kind of systems that need
some kind of user support, and we are planning to use it
for various applications and Web services in the future.

% Unlike existing smart IDEs for supporting programming tasks,
% {\EH} framework can be used in wide range of situations
% where translation-based help is required.
% 
% Using the powerful and flexible help system ``{\EH}''
% constructed on the generate-and-filter algorithm, where
% the system generates all the possible expressions of
% help entries expanded from regular expressions,
% while the output expressions are filtered by search keywords using
% an efficient approximate pattern matching algorithm.
% 
% Since the data format is simple and the search algorithm is fast and flexible,
% developers can easily publish useful help data, while
% users can have bigger chances of finding an appropriate
% data from vague knowledges.

>>>>

\def\HL{\textsf{HelpLine}}
\def\HF{\textsf{Helpfeel}}
\def\GIT{\texttt{git}}
\def\ES{\textsf{ExpandSearch}}
\def\SB{\textsf{Scrapbox}}
\long\def\tt#1{\texttt{#1}}
\long\def\stt#1{\texttt{\fontsize{9pt}{0pt}\selectfont{#1}}}
\long\def\sf#1{\textsf{#1}}
\long\def\ssf#1{\textsf{\fontsize{9pt}{0pt}\selectfont{#1}}}
\long\def\qtt#1{``\tt{#1}''}   % quote tt
\long\def\sqtt#1{``\stt{#1}''} % small quote tt
\long\def\qsf#1{``\sf{#1}''}
\long\def\sqsf#1{``\ssf{#1}''}
\long\def\qit#1{``\textit{#1}''}
\long\def\smallfont{\fontsize{9pt}{0pt}\selectfont}

@@

  As we have shown before, one of the big reasons why we fail to find a document is that
  the user's search keyword does not exist in the document.
  Providing entries for {\ES} can solve the problem, but

@@

% [[ExpandSearchの実例]]
%  まず実例を紹介する。実装はあとで。[[評価実験にもなっている。]]
% [[実例1]] ExpandHelpの実際の利用
%  ScrapboxというWiki上にいろんな表現を用意しておく
%  Helpfeel
%   PayPayフリマなどですごく効率があがった
%  実際これによりヘルプ問い合わせは劇的に減る (出典: Helpfeel)
% [[実例2]] 検索インタフェースの融合
%  マイHelpfeel
%  検索をひとつの方法に統合する
%   検索方法が複数だと面倒臭い
%    ググって出なければ逆引き辞典を検索する、みたいなのは面倒
%   同じ検索インタフェースでいろんなところを探すほうが簡単である
%   どこにメモしたか忘れて困ることがなくなる
%  自分のデータが増えていく状況のグラフを書ける!
% 
% [[実例3]]
%  gitのヘルプ - コマンドラインで動くもの
%   パラメタを指定して実行につなげることすらできる

We created the GitHelp system using {\ES}, so that git users can easily
remember command options and use it without perfectly remembering the git commands.

We implemented the HelpLine system
with which a user can translate his vague intention in various languages
into a complete {\GIT} command
using the {\ES} framework.

\begin{figure}[h]
  \vbox{
    \begin{verbatim}
      $ git diff HEAD^^ README.md
      $
    \end{verbatim}
  }
  \caption{Invoking \stt{git diff}.}
  \label{gitdiff}
\end{figure}

If HelpLine is installed,
the user can type a special shortcut key
(e.g. \texttt{Ctrl-J})
to invoke HelpLine after typing \sqtt{git RE 2} to see how he can
perform the task.

\begin{figure}[h]
  \includegraphics[width=9cm,bb=0 0 900 600]{../../GitHelp/paper/figures/example1.png}
  \caption{Invoking {\HL} after typing \stt{git read 2}.}
  \label{example1}
\end{figure}

Here, various candidate entries with descriptions and command strings are listed,
just like text input support systems for non-English languages.
One of the entries says
``\ssf{Compare} \stt{README.md} \ssf{with the one from 2 versions before}'',
and if the user thinks that's what he wants to do,
he can select the entry by typing arrow keys and the enter key.
Then the user's input string is replaced by the right command string
that satisfies the user's need.

When the user types the shortcut key
after typing \sqtt{git sh reed 3},
approximate pattern matching is automatically performed, and
entries related to \stt{README.md} file are listed because
\sqtt{reed} matches \sqtt{README.md} with one error.

\begin{figure}[h]
  \includegraphics[width=9cm,bb=-100 0 800 550]{../../GitHelp/paper/figures/example2.png}
  \caption{Invoking {\HL} after typing \stt{git sh reed 3}.}
  \label{example2}
\end{figure}

A Japanese {\GIT} user can do the same thing just like
English-speaking users (Figure \ref{example3}).
He can use the term \qtt{表}, etc. to find how he can perform the job.

\begin{figure}[t]
  \includegraphics[width=12cm,bb=-100 -100 1190 766]{../../GitHelp/paper/figures/example4.png}
  \caption{Invoking {\HL} in Japanese environment.}
  \label{example3}
\end{figure}

\begin{figure}[t]
  \centerline{\includegraphics[width=100mm,bb=-50 -50 1100 950]{../../GitHelp/paper/figures/scrapbox3.png}}
  \caption{A {\SB} page for \tt{git diff}.}
  \label{scrapboxpage}
\end{figure}

\subsection{OmniSearch}

OmniSearch is an implementation of ExpandSearch that runs on Chrome browser.
The URL window on Chrome is called omnibox,

@@

We have been applying ExpahdSearch for various customer support services on existing Web services.
The help system based on {\ES} is called {\HF}, and

{\HF} is a FAQ engine that supports users who do not have enough vocabulary for the Web services they want to use.

@@

Figure xxx shows an example {\HF} page that supports finding FAQs
for PayPay Free market run by Yahoo! Japan.
We provide the description on the Scrapbox wiki service,

@@

@@

\subsection{ExpandSearch}

A flexible search mechanism ``ExpandSearch'' is used in HelpLine.
%
The database used in ExpandSearch are provided as a set of data entries
consisting of a regular expression that represents description of the data entry
and a corresponding command pattern string.
A description string is used to produce natural language texts
that are easily understandable by users,
while command patterns represents the generated command string
corresponding to the description.
%
For example, a help entry for showing the difference between
current file and older file can be defined like this:

\begin{quote}
  \textbf{description}: \\
  \stt{Compare (\#\{files\}) with the one from (1|2|3|4) versions before}\\
  \textbf{command}: \\
  {\smallfont\verb|git diff $(git rev-list -n #{$2} HEAD -- #{$1})^ -- #{$1}|}
\end{quote}

@@

can be used for Japanese {\GIT} users.
In this case,
\sqsf{README.mdを1個前のものと比較する},
\sqsf{README.mdを2個前のものと比較する}, etc.
are used for the matching.

@@

Regular expressions are widely used for finding patterns in text strings
in modern programming languages and in the Unix environment.
In {\ES}, we use regular expressions for
generating various patterns of descriptions from a short specification.
For example, we use a short regular expression
\sqtt{(remove|delete|erase) (data|file)}
for representing expressions like
\sqsf{remove data},\sqsf{erase file}, etc.

Converting a regular expression to a state transition machine is a
straightforward task.
When we have a regular expression
\sqtt{Compare (README.md|index.html|package.json) with the one from (1|2|...|10) versions before}, 
we can convert it into a state transition diagram
shown in Figure \ref{statemachine1}.

\begin{figure}[htb]
\includegraphics[width=90mm,bb=0 0 571 126]{../../GitHelp/paper/figures/statemachine.pdf}
\caption{State transition diagram for a \stt{git} command description.}
\label{statemachine1}
\end{figure}

@@

Using the state transition diagram shown in Figure \ref{statemachine1},
{\ES} generates all the strings represented in the regular expressions,
and filter them by the pattern provided by the user.

We can generate texts from a state transition diagram by traversing nodes one by one.
Starting at the start node
(\raisebox{-2pt}{\includegraphics[height=10pt,bb=0 0 40 40]{../../GitHelp/paper/figures/startnode.pdf}})
in Figure \ref{statemachine1},
we can visit other nodes via edges and generate a tree of generated texts
shown in Figure \ref{gentree1}.
After visiting the initial node
\raisebox{-2pt}{\includegraphics[height=10pt,bb=0 0 40 40]{../../GitHelp/paper/figures/startnode.pdf}},
the system generates a string \sqsf{Compare} and proceeds to the next node.
In the second generation,
the system can add \sqsf{README.md}, \sqsf{index.html}, and \sqsf{package.json}
to \sqsf{Compare}, generating
\sqsf{Compare README.md}, \sqsf{Compare index.html}, etc.
The system can repeat finding edges from previously visited nodes,
and eventually generates all the strings described above.
Of course, it is impossible to generate all the strings
from a regular expression like ``\tt{(0|1)+}'' that represents infinite length of
strings consisting of \tt{0}s and \tt{1}s, so the generation should be
terminated at a certain generation.

\begin{figure}[htb]
\includegraphics[width=85mm,bb=0 0 643 398]{../../GitHelp/paper/figures/gentree1.pdf}
\caption{Generating a text tree from a state transition machine.}
\label{gentree1}
\end{figure}

@@

Similarly in our case,
it is not efficient to perform the matching operation
after generating all the texts from the regular expression,
and it is better to calculate the matching
at the time of generating each text.
We call it the \qit{generate-and-filter} strategy,
and implemented the algorithm in {\ES}.
Unlike simple puzzle problems where
conditions are strict and finding one solution is enough,
our goal is to find help description strings
that fits the query pattern while allowing errors.
For this goal,
the system should perform approximate pattern matching
without sacrificing processing speed.
%
We could implement flexible generate-and-filter by using a simple and efficient
approximate pattern matching algorithm based on the ``shifter algorithm''.

@@

\begin{figure}[h]
  \centerline{\includegraphics[width=50mm,bb=0 0 439 73]{../../GitHelp/paper/figures/readme1.pdf}}
  \caption{A state machine for \qsf{README}.}
  \label{readme1}
\end{figure}

@@

\begin{figure}[h]
  \centerline{\includegraphics[width=50mm,bb=0 0 439 73]{../../GitHelp/paper/figures/readme2.pdf}}
  \caption{After receiving \qsf{R}.}
  \label{readme2}
\end{figure}

@@

% \begin{figure}[htb]
%   \centerline{\includegraphics[width=30mm,bb=0 0 104 51]{figures/readme-mismatch.pdf}}
%   \caption{Matching error between \qsf{README} and \qsf{REEDEE}.}
%   \label{readme-reddy-mismatch}
% \end{figure}

@@

\begin{figure}[htb]
  \centerline{\includegraphics[width=60mm,bb=0 0 443 282]{../../GitHelp/paper/figures/readme-ambig.pdf}}
  \caption{A pattern matcher accepting 0-3 errors.}
  \label{shifterambig}
\end{figure}

@@

\begin{figure}[htb]
  \centerline{\includegraphics[width=60mm,bb=0 0 443 282]{../../GitHelp/paper/figures/readme-reedee.pdf}}
  \caption{Accepting \sqsf{REEDEE}'' using a matcher for \sqsf{README}.}
  \label{readme-reedee}
\end{figure}

@@

\begin{figure}[htb]
  \centerline{\includegraphics[width=50mm,bb=0 0 302 230]{../../GitHelp/paper/figures/RE_2.pdf}}
  \caption{A pattern matcher for \sqtt{REE 2}.}
  \label{RE_2}
\end{figure}

\begin{figure*}[bth]
\centerline{\includegraphics[width=110mm,bb=0 0 643 446]{../../GitHelp/paper/figures/gentree2.pdf}}
\caption{Matching statuses for \sqtt{REE 2} associated with text generation nodes.}
\label{gentree2}
\end{figure*}

@@

% \begin{figure*}[bt]
% \centerline{\includegraphics[width=146mm]{../../GitHelp/paper/figures/04ad7dee5679450e5390821745b5a0b7.png}}
% \caption{A portion of the help data in Ruby.}
% \label{helpdata}
% \end{figure*}

@@

The data used in {\HL} are represented as ``{\SB}'' documents
shown in Figure \ref{scrapboxpage}.
%
{\SB} is a general-purpose real-time Wiki system for data sharing.
{\SB} users can edit the contents of Wiki pages directly
on Web browsers just like using text editors.

% \begin{figure}[htb]
% \begin{verbatim}
% \end{verbatim}
% % \centerline{\includegraphics[width=100mm,bb=0 0 1428 1288]{../../GitHelp/paper/figures/scrapbox1.png}}
% \centerline{\includegraphics[width=100mm,bb=-50 -50 1000 900]{../../GitHelp/paper/figures/scrapbox1.png}}
% \caption{A {\SB} page for \tt{git diff}.}
% \label{xxxxx}
% \end{figure}

This page shows how to use \sqtt{git diff}, and
the page contains command specifications in {\ES} format
in addition to the documentation.

@@

Also, since the database is on the Wiki page, any member of the
Wiki can correct the document or add additional {\HL} specifications.
When a user could not get a good support from {\HL}, he can add
{\ES} specifications to the {\SB} document himself
so that he and other people can get better support
from {\HL} next time.

@@

There have long been many researches on
intelligent help systems\cite{Delisle:2002:UIH:606412.606415},
but few number of projects seem to be going on these days,
maybe because now we can use the Internet for getting intelligent help from
real people,
either by searching existing Web pages or 
by asking in user forums like StackOverflow\footnote{
  \textsf{https://stackoverflow.com/}
}.
Information on the net is rich these days, and we can easily
find somebody who can give good answers to our questions.
This is a good news, but 
asking many trivial questions on the net is not considered to be a
good manner, and
using a powerful and flexible local help system like {\ES} is
preferable most of the time.

@@

\begin{figure}[H]
  % \includegraphics[width=8cm,bb=0 0 976 670]{../../GitHelp/paper/figures/nyuuryoku-ime.png}
  \centerline{\includegraphics[width=8cm,bb=0 0 976 670]{../../GitHelp/paper/figures/nyuuryoku-ime.png}}
  \caption{An IM for Japanese text input.}
  \label{gyaim}
\end{figure}

@@

IMs are very popular in the modern computing environment in the world
and it is very common for people to 
use translation systems for using computers.
%
The behavior of {\HL} is similar to conventional IMs, and
integration of multiple IM-like systems should be challenged in the future.

@@

Gitsome\footnote{\textsf{https:{\slash}{\slash}github.com{\slash}donnemartin{\slash}gitsome}}
helps {\GIT} users by
dynamically showing possible arguments and related manuals on the Unix shell,
just like {\HL} does.
The goal of Gitsome is almost the same as {\HL} and we agree with its concept,
but Gitsome does not support flexible approximate matching and
help data sharing.

@@

Han's Abbreviation Completion system\cite{Han:2009:CCA:1747491.1747530}
can generate a code snippet from abbreviation strings give by the user.
For example, a code snippet like \sqtt{chooser. showOpenDialog()}
can be generated from strings like
\sqsf{ch} and \sqsf{opn}, using the code database and HMM.
It can be very useful as a shorthand for handling long names,
but users should have a vague knowledge about the correct names
(e.g. \sqtt{chooser}, \sqtt{dialog}),
and large code example corpus should exist before being able to
create the database.
{\ES} database can be created by hand at the time of the system development
and no corpus is required.

@@

Using BluePrint\cite{Brandt:2010:EPI:1753326.1753402}
as a plugin for Adobe Flex Builder,
users can search sample codes from the Web and use it immediately.
%   サンプルコードをすぐ参照して利用できる[IDE]
%
HelpMeOut\cite{Hartmann:2010:OPS:1753326.1753478} tells users
how to handle compile errors,
based on the people's experiences of handling compile errors.
%
Resources on the net are precious, and such data can be
easily incorporated to {\ES} databases.

@@

Since the translation mechanism of {\ES} is simple and flexible,
it can be used for a wide range of application domains where
intelligent help is required.
{\ES} is actually used as the help page for
one of our Web services, hoping that
novice users can easily find the feature they need.
When a user submits a query that includes vocabularies
not in the {\ES} document,
we are able to add them to the {\SB} database easily.

Figure \ref{mac1} and Figure \ref{mac2} shows how
{\ES} can be used as a launcher for MacOS.
Like {\HL}, users can execute concrete commands only by
showing small fragments of their intentions to the system.

\begin{figure}[h]
  %\centerline{\includegraphics[width=8cm,bb=0 0 397 247]{../../GitHelp/paper/figures/clock.png}}
  \centerline{\includegraphics[width=8cm,bb=0 0 300 200]{../../GitHelp/paper/figures/mac1.png}}
  \caption{Using {\ES} in the menu bar of MacOS.}
  \label{mac1}
\end{figure}

\begin{figure}[h]
  %\centerline{\includegraphics[width=8cm,bb=0 0 392 185]{../../GitHelp/paper/figures/mac2.png}}
  \centerline{\includegraphics[width=8cm,bb=0 0 300 130]{../../GitHelp/paper/figures/mac2.png}}
  \caption{Using {\ES} in the menu bar of MacOS.}
  \label{mac2}
\end{figure}

@@

Using a command shell,
users have to enter a command first and enter options and arguments after that.
Using a GUI desktop,
users can right-click a data icon to show a menu,
and select what he wants to do from the menu.
Switching between command-oriented usage pattern and
data-oriented usage pattern is sometimes confusing.
Using {\ES}, users can find what they can do
either by specifying commands or by specifying data, 
without worrying about the order.

@@

An advantage of using a regular expression is that
it is fairly easy for users to write description texts.
People can easily write a help description like
\sqtt{(Start|Run) Firefox browser}
without having a knowledge of automata or formal grammar.
We can use arbitrary texts for the database of {\ES}.
For example,
we can collect hundreds of books titled ``Windows tips'' from the market
and convert all the title of the tips into help data of {\ES}.

@@

We proposed the ``translation paradigm'' for bridging the gap between
users' intention and actual operations.
%
We have introduced a general-purpose flexible framework {\ES}
that can translate fragments of user's vague intentions into
concrete command strings required to control computers and
other complex artifacts.
We showed the principles and applications of {\ES} by using it
for {\HL}, a help system for supporting {\GIT} users
based on the shared database that any user can edit to share
translation knowledge between users.
%
{\ES} framework is useful for any kind of systems that need
some kind of user support, and we are planning to use it
for various applications and Web services in the future.

% Unlike existing smart IDEs for supporting programming tasks,
% {\ES} framework can be used in wide range of situations
% where translation-based help is required.
% 
% Using the powerful and flexible help system ``{\ES}''
% constructed on the generate-and-filter algorithm, where
% the system generates all the possible expressions of
% help entries expanded from regular expressions,
% while the output expressions are filtered by search keywords using
% an efficient approximate pattern matching algorithm.
% 
% Since the data format is simple and the search algorithm is fast and flexible,
% developers can easily publish useful help data, while
% users can have bigger chances of finding an appropriate
% data from vague knowledges.
